---
title: "Fun with Strava Data"
author: "R Package Build"
date: "5/24/2021"
slug: functional-programming-with-strava-data
categories: R
tags:
- R
- Strava
---

## Let's have fun with your Strava data!

This blog post is intended to provide an additional example of the ways personal data can be used. Our final product will be a ridgeline plot a la Joy Division's *Unknown Pleasures*. Slap it on a t-shirt, throw it on a mug, and fool your friends! Or most likely strangers! Because your friends probably already know your musical preferences!

Them: Oh, you're a Joy Division fan? 

You: **No!** I just love cycling and data!

```{r Final product}

```

## Alright friends

First things first, open up RStudio and start a brand new R Markdown file. We're going to use quite a few packages, most of which have been introduced in our other blog posts (link here). Here's what we'll need:

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(purrr)
library(repurrrsive)
library(here)
library(janitor)
library(lubridate)
library(rStrava)
library(plyr)
```
