---
title: "Parallel Iterations of Strava Data"
author: "Makayla Whitney, Joe Swinehart, Janette Avelar, David Fainstein"
date: "5/19/2021"
slug: functional-programming-with-strava-data
categories: R
tags:
- R
- Strava
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#note: include = FALSE and echo = FALSE for now, but it will still print messages and can be coerced to show full chunks of code if we desire

library(tidyverse)
library(purrr)
library(repurrrsive)
library(here)
library(janitor)
library(lubridate)

```

Strava is an excellent way to keep track of physical activity on an individual basis. 

We will begin by reading in a batch of data from one individual.

```{r firststep}
#reading in data for sandbox
strav_data <- read_csv(here::here("content/post/2021-04-16-functional-programming-with-strava-data/data", "strav_csv.csv"))

#initial function for tidying Stravadata
tidydata <- strav_data %>% 
  select(where(~length(unique(.)) > 1)) %>%
    # selecting unique values
  clean_names() %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
    # rounding values to remove clutter for visualization
  mutate(type = as.factor(type)) %>%  
  dplyr::rename(act_type = type) %>% 
  separate(start_date_local, c("date","time"), sep = " ") %>% 
  select(-start_date) %>% 
    #separating out date & time; excluding multiple dates and times
  filter(elapsed_time > 0,
         max_speed > average_speed)

# If this is basically the same cleaning, you could export a cleaned version of your data file and put it in the data folder, then you can just pull from that in your other scripts?
```

Then we will create a function that allows us to turn dates into days of the week and times into periods during the day. This will help us to categorize activities by days of the week and time periods within the day.

```{r secondstep}

d <- tidydata %>%
  select(date, time, act_type)


daysoftheweek <- function(d, date) {
  date <- d(date = as.Date(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) # I think r is confused here because date is being used as a function, not a dataset in this code
  weekday <- strftime(date$date, "%A")
  print(weekday)
}

byact <- weeklydata %>%
  group_by(act_type) %>%
  nest()


```

This is an iteration of weekly activity Monday - Sunday categorized by time of day. 

```{r thirdstep}

````

This is another iteration of weekly activity Monday - Sunday categorized by time of day.

```{r fourthstep}

#saving plots
#create a directory
fs::dir_create(here::here("final_plots", "eugeneroads"))
paths <- here::here("final_plots", "eugeneroads", glue("{eugeneroads}.png"))

#trying to find a way to fit this in
walk2(paths, final_plots$eugeneroads, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)

# Great idea to get the plots by the day of the week. That's a very natural way to want to see your data
````

