---
title: "Parallel Iterations of Strava Data"
author: "Makayla Whitney, Joe Swinehart, Janette Avelar, David Fainstein"
date: "5/19/2021"
slug: functional-programming-with-strava-data
categories: R
tags:
- R
- Strava
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#note: include = FALSE and echo = FALSE for now, but it will still print messages and can be coerced to show full chunks of code if we desire

library(tidyverse)
library(purrr)
library(repurrrsive)
library(here)
library(janitor)
library(lubridate)
## Glue is not loaded for later in the script
library(glue)

```

Strava is an excellent way to keep track of physical activity on an individual basis. 

## I could use a little explanation here about what the outcomes of this post are. Is this to show how to plot out activities by week and time? 

We will begin by reading in a batch of data from one individual.

```{r firststep}
#reading in data for sandbox
strav_data <- read_csv(here::here("content/post/2021-04-16-functional-programming-with-strava-data/data", "strav_csv.csv"))

#initial function for tidying Stravadata
tidydata <- strav_data %>% 
  select(where(~length(unique(.)) > 1)) %>%
    # removing columns with non-varying values
  clean_names() %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
    # rounding values to remove clutter for visualization
  mutate(type = as.factor(type)) %>%  
  dplyr::rename(act_type = type) %>% 
  separate(start_date_local, c("date","time"), sep = " ") %>% 
  select(-start_date) %>% 
    #separating out date & time; excluding multiple dates and times
  filter(elapsed_time > 0,
         max_speed > average_speed)


```

Then we will create a function that allows us to turn dates into days of the week and times into periods during the day. This will help us to categorize activities by days of the week and time periods within the day.

```{r secondstep}

d <- tidydata %>%
  select(date, time, act_type)

# Having trouble getting this to run
daysoftheweek <- function(d, date) {
  date <- d(date = as.Date(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
  weekday <- strftime(date$date, "%A")
  print(weekday)
}

## Is this doing what you want?
daysoftheweek <- function(d, date) {
  d <- d %>% 
    mutate(date = as.Date(date),
           weekdays = weekdays(date))
}

sample <- daysoftheweek(d, date)

# I think you are trying to pull in the `d` dataset from above?
byact <- d %>%
  group_by(act_type) %>%
  nest()


```

This is an iteration of weekly activity Monday - Sunday categorized by time of day. 


```{r thirdstep}

````

This is another iteration of weekly activity Monday - Sunday categorized by time of day.

```{r fourthstep}

#saving plots
#create a directory
fs::dir_create(here::here("final_plots", "eugeneroads"))
paths <- here::here("final_plots", "eugeneroads"), glue("{eugeneroads}.png"))

#trying to find a way to fit this in
walk2(paths, final_plots$eugeneroads, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)

````

