---
title: "Parallel Iterations of Strava Data"
author: "Makayla Whitney, Joe Swinehart, Janette Avelar, David Fainstein"
date: "5/19/2021"
slug: functional-programming-with-strava-data
categories: R
tags:
- R
- Strava
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#note: include = FALSE and echo = FALSE for now, but it will still print messages and can be coerced to show full chunks of code if we desire

library(tidyverse)
library(purrr)
library(repurrrsive)
library(here)
library(janitor)
library(lubridate)

```

Strava is an excellent way to keep track of physical activity on an individual basis. 

We will begin by reading in a batch of data from one individual.

```{r firststep}
#reading in data for sandbox
strav_data <- read_csv(here("content/post/2021-04-16-functional-programming-with-strava-data/data", "strav_csv.csv"))

#initial function for tidying Stravadata
tidydata <- strav_data %>% 
  select(where(~length(unique(.)) > 1)) %>%
    # selecting unique values
  clean_names() %>% 
  mutate_if(is.numeric, ~round(., 2)) %>% 
    # rounding values to remove clutter for visualization
  mutate(type = as.factor(type)) %>%  
  dplyr::rename(act_type = type) %>% 
  separate(start_date_local, c("date","time"), sep = " ") %>% 
  select(-start_date) %>% 
    #separating out date & time; excluding multiple dates and times
  filter(elapsed_time > 0,
         max_speed > average_speed)


```

Then we will create a function that allows us to turn dates into days of the week and times into periods during the day. This will help us to categorize activities by days of the week and time periods within the day.

```{r secondstep}

d <- tidydata %>%
  select(date, time, act_type)


daysoftheweek <- function(d, date) {
  date <- d(date = as.Date(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")))
  weekday <- strftime(date$date, "%A")
  print(weekday)
}


byact <- weeklydata %>%
  group_by(act_type) %>%
  nest()


```

This is an iteration of weekly activity Monday - Sunday categorized by time of day. 

```{r thirdstep}

````

This is another iteration of weekly activity Monday - Sunday categorized by time of day.

```{r fourthstep}

#saving plots
#create a directory
fs::dir_create(here::here("final_plots", "eugeneroads"))
paths <- here::here("final_plots", "eugeneroads", glue("{eugeneroads}.png"))

#trying to find a way to fit this in
walk2(paths, final_plots$eugeneroads, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)

````

### Overall comment by Shijing: 

I think how you incorporate comment as explanation for your code is really friendly for viewers, especially for those who are less confident with coding. The language use for the blog (in `jd_post.Rmd`) is intriguing to read. The steps are broken down nicely, and linking blog posts together for your blog is a good idea for viewers to navigate. One potential improvement in the future could be displaying and explaining outputs briefly (or at least a part of a output by using `head()`) to complement your explanation of code so that people know what to expect if they want to adapt your code. I never use `walk2()` before, which is something new I learned! 
